---
title: "Tables of adjusted stop delays"
output: html_notebook
---

```{r}
library(tidyverse)
library(lubridate)
```
### This code takes the .csv files that were constructed in adjusted_delays_further.Rmd and fills them with the count of the number of delays greater than several increasingly large threshold values.  One must specify the number of weeks of delay data one would like to use, and the values of the delay thresholds in minutes.

#### The function delays() extracts the delay increment at each haltstelle, for each time that a vehicle stops at the haltstelle.  

```{r}
#########################################################################################
################### Delay Increments At Stops  #################
#########################################################################################
# This function will return a tibble (tidyverse dataframe) of the delays greater than
# a certain integer, measured in minutes.  Minute values are rounded down from seconds.
#  PARAMETERS:
# small_tib -- a fahrzeitensollist .csv dataset from VBZ
# out_tib -- the name of an empty tibble
# work.line -- the bus or tram line of interest
# min_delay_von_min -- the minimum delay time for delays at the von stop
#
# Requires: tidyverse or dplyr library
#
# Contributers:  Peter B. Pearman  pbpearman@gmail.com
#
##########################################################################################
# small_tib  --a VBZ delay dataset
# out_tib    --the output dataset
# work.line  --the tram or bus line in question
# min_delay_seg_min --the threshold increment of additional delay on a segment
# min_delay_von_min --the threshold increment of additional delay at the 'von' stop

delays <- function(small_tib,work.line,direction,min_delay_von_min){
  small_tib$halt_kurz_von1 <- as.character(small_tib$halt_kurz_von1)
  delay2 <- small_tib %>%                                   #This is left selecting most variables to ease further development
    
        # delay at the station
    
    mutate(soll_at_von = soll_ab_von - soll_an_von,
         ist_at_von = ist_ab_von - ist_an_von,
         delay_von_min = (ist_at_von - soll_at_von)/60) %>%
  
                                            # now filter out lines that do not have at least one delay that is greater than the necessary minimum
    filter(delay_von_min >= min_delay_von_min, linie == work.line, richtung == direction)  
                                            # Could this be developed with a eval(parse(text=paste())) to filter on a condition
                                            # that is supplied to the function as a string argument?
  return(delay2)
}
```

#### The nested loops below cycle through the weekly delay dataset names in *temp*, which is a vector of strings, the lines in *worklines*, each direction, and each stop (the rows in the tibble *outfile*) and updates the additional number of delays greater than the threshold for each stop for the line. There is a separate *outfile* for each line, which is saved.  The *outfile* data sets are constructed using the code in adjusted_delays_further.Rmd, which is also in this repository.


```{r data_load, cache=TRUE, autodep=TRUE}
temp <- list.files('../data/fahrzeiten_data')
temp <- temp[1:52]      # the delay data set relative names
work.lines <- read_csv("../data/other_data/unique_lines.csv")  # a data set of the lines
min_delay_von_min = c(1.5,2,3,4,5,6)  #thresholds to use, currently 6 in number
data2 <- tibble()    # a summarized group_by object that has been filtered using a delay threshold
out_tib <- tibble()  #the data set for a line in which the number of delays at each stop and threshold is tallied
for (i in temp){
  print(i)
  small_tib <- as_tibble(read.csv(paste('../data/fahrzeiten_data/',i,sep=""),stringsAsFactors = FALSE))
  for (work.line in work.lines$lines) {
    outfile <- paste("../data/stop_delays/stops_delays_52_weeks_line_",work.line,".csv",sep='')
    
    #sink1 <- file(description = "messages.txt",open="a")
    #sink(file=sink1,append=TRUE)
    #sink(sink1,type="message",append = TRUE)
    print(outfile)
    out_tib <- read_csv(outfile,col_types = cols())
    for (direction in c(1,2)) {
      for (min1 in min_delay_von_min) {
       data2 <- delays(small_tib,work.line,direction,min_delay_von_min = min1) %>%
         group_by(halt_kurz_von1) %>%
         summarize(num_delays = n())
       if ((dim(data2)[1]==0)==TRUE) break
       #print(c(data2$num_delays,data2$halt_kurz_von1))
       if ((min1 == 1.5)==TRUE) min1 <- 1
       for (k in 1:length(data2$halt_kurz_von1)) {
         colnam <- paste("del_",min1,"_",direction,sep="")
         a <- out_tib[[colnam]][which(out_tib$stops==data2$halt_kurz_von1[k])]
         b <- data2$num_delays[k]
         out_tib[[colnam]][which(out_tib$stops==data2$halt_kurz_von1[k])] <- a + b 
       }
      }
    }
    #sink(type="message")
    #sink()
    #close(sink1)
    write_csv(out_tib,outfile)
  }
}


```
```{r}
head(out_tib)
```

