---
title: "Visualize Transit Delay Data"
output:
  html_document: default
---

#### This visualization was initiated at the Open Data Day Hackathon in Zürich, 4 March 2017.

#### The original delay data come from data collected by the Verkehrsbetriebe Zürich (VBZ) and are available pubically from the Open Data Portal of [Stadt Zürch Open Data](https://data.stadt-zuerich.ch/dataset?sort=score+desc%2C+metadata_modified+desc&tags=vbz)

#### You can find the source code and other files [here](https://github.com/OpenDataDayZurich2016/visualization_delays)

#### The data represent the number of delays greater than the stated threshold.  The delays are tallied based on the increment in delay that occurred at a stop, independent of whether the vehicle arrived at the stop on time or not.  Negative delays, in which a vehicle stayed at a stop for less than the planned elapsed time, and thereby made headway on the schedule, were not counted.  

#### The source code can be easily modified to count delays greater than a threshold in both directions, or use a higher threshold, in minute increments, up to six minutes.  All maps show data for one direction only.

### ==================================================================

```{r include=FALSE}
library(tidyverse)
library(lubridate)
library(leaflet)
library(htmlwidgets)
library(htmltools)
```

```{r, include=FALSE}
lines <- c(2,7,9,10,14,33,72)

popup=c("stops","halt_lang")

# addtiles() function fix found here: https://github.com/rstudio/leaflet/issues/192
addTiles2 = function (map, urlTemplate = "http://{s}.tile.openstreetmap.org/{z}/{x}/{y}.png",
attribution = NULL, layerId = NULL, group = NULL, options = tileOptions())
{
options$attribution = attribution
if (missing(urlTemplate) && is.null(options$attribution))
options$attribution = paste("© OpenStreetMap",
"contributors, CC-BY-SA")
invokeMethod(map, getMapData(map), "addTiles", urlTemplate,
layerId, group, options)
}

# This loop creates and saves a widget for each dataset specified in 'lines'
for (i in lines){
  df <- read_csv(paste('../data/stop_delays/stops_delays_52_weeks_line_',i,'.csv',sep='')) %>%
    filter(!stops %in% c('DEP2','DEP4','DEP7','DEP8','GAR6','FRAF07')) %>%
    mutate(content = paste(stops,halt_lang,'count =',del_1_1,sep=" "))
  
  pal <- colorBin(palette = "Reds", domain=df$del_1_1, 6, pretty = FALSE)

  m <- leaflet(df) %>% addTiles2() %>% setView(lng=8.5402,lat=47.3778,zoom=12) %>%
    addCircles(~lon,~lat,label = ~content, #~htmlEscape(content) # popup= ~halt_lang, goes in addCircles
             radius = 150, stroke=TRUE,color="Black",weight=1, fillColor = pal(df$del_1_1),
             fillOpacity = 0.8) %>%
    addLabelOnlyMarkers(~lon,~lat,label = ~content)
    
  m <- m %>%
    addLegend("bottomright", pal=pal, values= ~del_1_1, title = 'Delays > 1.5 min', opacity =0.8)

  saveWidget(widget = m, file= paste("./line_",i,".html",sep=''),selfcontained = TRUE)
  eval(parse(text = paste('m_',i,'<- m',sep='')))
}
```
## Which Tram Stops have more delays?
## Here are data for Tram 2
```{r echo = FALSE}
m_2
```



## Tram 7 Number of Delays
### Greater that 1.5 minutes

```{r echo= FALSE}
m_7
```

## Tram 9 Number of Delays

### Greater than 1.5 minutes


```{r echo = FALSE}
m_9
```

## Tram 10 Number of Delays

### Greater than 1.5 minutes
```{r echo = FALSE}
m_10
```

## Tram 14 Number of Delays

### Greater than 1.5 minutes
```{r echo = FALSE}
m_14
```

## Bus 33 Number of Delays

### Greater than 1.5 minutes
```{r echo = FALSE}
m_33
```

## Bus 72 Number of Delays

### Greater than 1.5 minutes
```{r echo = FALSE}
m_72
```

